NTIRE 2023 Real-Time Super-Resolution

### 2023-03-22 NTIRE 2023 RTSR Factsheet/main.tex
final
最终保存

\begin{table}[]
    \centering
    \resizebox{\textwidth}{!}{
    \begin{tabular}{c|c|c|c|c|c|c|c}
        Track & Input & Training Time & Attention & Quantization & \# Params. (M) & GPU  \\
        \hline
        1 & (678,1020,3) & 16h & No & No & 0.0299 Million & RTX 3070 8G \\
        2 & (512,680,3) & 16h & No & No & 0.0629 Million & RTX 3070 8G \\
    \end{tabular}
    }
    \caption{FILL THIS TABLE PLEASE}
    \label{tab:my_label}
\end{table}

@@

Negative impression: Instructions are not clear (e.g. there are some posts in the forum saying that they cannot find the test set, but none of the organizers respond).

>>>>

\begin{table}[]
    \centering
    \resizebox{\textwidth}{!}{
    \begin{tabular}{c|c|c|c|c|c|c|c}
        Track & Input & Data range & Training Time & Attention & Quantization & \# Params. (M) & GPU  \\
        \hline
        1 & (678,1020,3) & 255 & 16h & No & No & 0.0299 Million & RTX 3070 8G \\
        2 & (512,680,3) & 255 & 16h & No & No & 0.0629 Million & RTX 3070 8G \\
    \end{tabular}
    }
    \caption{FILL THIS TABLE PLEASE}
    \label{tab:my_label}
\end{table}

@@

Negative impression: There are some posts in the forum saying that they cannot find the test set, but none of the organizers respond.
